\huge Tor's Usability for Censorship Circumvention

### 2016-04-29 pets2017-paper/pets2017-paper.tex
Say something about simple.wikipedia.org.

>>>>

We blocked en.wikipedia.org, the target of the experiment,
as well as other language-specific subdomains such as
de.wikipedia.org and fr.wikipedia.org.
We neglected, however, to block the Simple English Wikipedia
at simple.wikipedia.org, which one participant found,
thinking they had completed the task.
% E2-OLD-X04-20160330-181928
